---
title: "Analysis_Questions"
author: "Pascale Goertler, Aaron Angel, Dylan Stern"
date: "2023-03-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis Questions

# Initial Brainstorming

Look for patterns related to geography and types of involved actors and application type (restoration, climate change, water management, etc.) 

Look for patterns in characterization/description of TK and year (possibly relating year to key words like “holistic” “spiritual” “place-based” “relationship” etc.) 

Something about relationship, reciprocity, respect – maybe even just quantifying how often they appear? 

Negative words/connotation of native authors vs. non-native authors 

Look for ~ “success” (qualitative). Knowledge + colonialism. Where are definitions of TK and WS?  

Progression over years of new vocabulary (using our glossary). Similar to Sean’s Evolution of words over time. 

## Question 1

```{r question 1, echo=FALSE}

```

## Question 2

```{r question 2, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
